Number recognition for use in a Sudoku solver

### 2012-03-15 doc/icml2010stylefiles/paper.tex
- fixed paper
- lr gridsearch results added
fix

\begin{abstract}
The goal of this work is to implement number recognition for a Soduko solver.
First we will describe the generation of synthetic data, in this case labelled images of numbers.
Then we compare different machine learning techniques for supervised learning using the generated data.
Once the training is complete, images of real Sudokus are captured using a webcam and preprocessed to be predicted by the learned models. We evaluate the different approaches by analyzing their performance on different data sets.
\end{abstract}

@@

\section{Overview}
Figure \ref{fig:overview} shows the basic data flow and the participating data manipulators. First of all we generate data by sampling position, rotation, size and color of a number and place it based on these values on a white 20x20 pixel image. Examples of 9 such generated images are shown in Figure \ref{fig:generated_numbers}.The corresponding labels are defined by the name of the folder the images are stored in.
\begin{figure}[ht]
	\centerline{\includegraphics[scale=0.25]{../examples}}
	\caption{Examples of generated numbers}
	\label{fig:generated_numbers}
\end{figure}
These images are preprocessed (applying greyscale) by an octave script and written to an input matrix and a target vector. All pixels of one image are encoded in one row of the input matrix and the corresponding label is stored in the row of the target vector. The data is dumped to a ``cache.mat'' file which allows us to apply many different tools and programming languages to the dataset. In our case we use it in python and octave.
% trim=l b r t
\begin{figure}[ht]
	\centerline{\includegraphics[width=\columnwidth, trim=25 30 25 30]{../overview}}
	\caption{Overview}
	\label{fig:overview}
\end{figure}
The input matrix $X^{n\text{x}400}$ and the target vector $y$ are the inputs for training NN, SVM and LR, as described in Section \ref{training}. After training, the learned models/parameters are saved in ``.mat'' files that can be loaded by the number prediction. The other input for number prediction is an input matrix of the same form as $X$ with a row entry for each Sudoku field that was detected to contain a number. This implies that we do not train our models to detect empty fields. We could detect empty fields with high accuracy by performing some preprocessing steps on the images (filling borders, adjusting thresholds etc.) thus applying a machine learning technique does not seem appropriate for this task.

>>>>

\begin{abstract}
The goal of this work is to implement number recognition for a Sudoku solver.
First we will describe the generation of synthetic data, in this case labeled images of numbers.
Then we compare different machine learning techniques for supervised learning using the generated data.
Once the training is complete, images of real Sudokus are captured using a webcam and preprocessed in order to be recognized by the learned models. We evaluate the different approaches by analyzing their performance on different data sets.
\end{abstract}

@@

\section{Overview}
Figure \ref{fig:overview} shows the basic data flow and the participating data manipulators. First of all we generate data by sampling position, rotation, size and color of a number and place it based on these values on a white 20x20 pixel image. Examples of 9 such generated images are shown in Figure \ref{fig:generated_numbers}. The corresponding labels are defined by the name of the folder the images are stored in.
\begin{figure}[ht]
	\centerline{\includegraphics[scale=0.25]{../examples}}
	\caption{Examples of generated numbers}
	\label{fig:generated_numbers}
\end{figure}
These images are preprocessed (applying greyscale) by an octave script and written to an input matrix and a target vector. All pixels of one image are encoded in one row of the input matrix and the corresponding label is stored in the row of the target vector. The data is dumped to a ``cache.mat'' file which allows us to apply many different tools and programming languages to the dataset. In our case we use it in python and octave.
% trim=l b r t
\begin{figure}[ht]
	\centerline{\includegraphics[width=\columnwidth, trim=25 30 25 30]{../overview}}
	\caption{Overview}
	\label{fig:overview}
\end{figure}
The input matrix $X^{n\text{x}400}$ and the target vector $y$ are the inputs for training NN, SVM and LR, as described in Section \ref{training}. After training, the learned models/parameters are saved in ``.mat'' files that can be loaded by the number prediction. The other input for number prediction is an input matrix of the same form as $X$ with a row entry for each Sudoku field that was detected to contain a number. This implies that we do not train our models to detect empty fields. We could detect empty fields with high accuracy by performing some preprocessing steps on the images (filling borders, adjusting thresholds etc.) thus applying a machine learning technique does not seem appropriate for this task.
